%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Shantanu}{Verma}{ \urlstyle{same}\
\href{mailto:shantanuverma12@gmail.com}{shantanuverma12@gmail.com} | +91-8447799732
}

\href{https://www.linkedin.com/in/shantanuv12/}{https://www.linkedin.com/in/shantanuv12/}

\begin{center}
\huge\color{subheadings}\custombold{Sophomore In Computer Science And Engineering }
\end{center}

\vspace{\topsep}
\section{Education}
\runsubsection{Indian Institute of Technology,Delhi}
\descript{| B.Tech in Computer Science and Engineering}
\location{Expected Jul 2020 | Hauz Khas, New Delhi} 
\textbullet{} CGPA: 7.588 (Out of 10)
\sectionsep

\runsubsection{Nehru World School}
\descript{| CBSE 12th Grade}
\location{Completed April 2016 | Ghaziabad,Uttar Pradesh}
\textbullet{} Percentage: 94.4 (Out of 100)  
\sectionsep

\runsubsection{Nehru World School}
\descript{| CBSE 10th Grade}
\location{Completed April 2014 | Ghaziabad,Uttar Pradesh}
\textbullet{} CGPA: 10 (Out of 10)  
\sectionsep


\vspace{\topsep}
\section{Projects}

\runsubsection{Image Compressor }
\descript{| Prof. Mausam }
\location{Sep 2017 – Oct 2017}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Implemented a simple Image Compression Algorithm of Greyscale Images using Arrays and Linked Lists.
\item Implemented various functions which could manipulate individual pixels of image as well as whole images using various logics.
\end{tightemize}
\sectionsep

\runsubsection{Multiplier Design}
\descript{| Prof. Anshul Kumar }
\location{Sep 2017 – Oct 2017}
\vspace{\topsep}
\begin{tightemize}
\item Implemented various Multplier designs using adders to create and find the most optimum multiplier. 
\item Multiplier was designed and implemented in VHDL. 
\end{tightemize}
\sectionsep

\runsubsection{Percolation}
\descript{| Independent Project}
\location{Jun 2017 – July 2017 }
\vspace{\topsep}
\begin{tightemize}
\item Percolation is an abstact process to model situations where in some given composite system comprised of randomly distributed sites like in a insulating or metallic materials. We try to figure out what fraction of material need to be metallic so that the composite system is a conductor or the given system Percolates. 
\item  Used monte-carlo simulation to calculate the percolation threshold.
\item The model was develped in Java. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RELEVENT COURSES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Relevent Courses}
\runsubsection{Computer Science}
\location{}
\begin{tightemize}
\item Algorithms and Data Structures, Discrete Mathematics, Digital Logic and System Design,Computer Architecture, Programming Languages, Design Practices
\end{tightemize}
\sectionsep

\runsubsection{Mathematics}
\location{}
\begin{tightemize}
\item Probability and Stochastic Processes, Linear algebra and Differential Equations, Calculus
\end{tightemize}
\sectionsep

\runsubsection{Online}
\location{}
\begin{tightemize}
\item Machine Learning(Coursera), Algorithms I (Coursera) 
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   SCHOLASTIC ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{\topsep}
\vspace{\topsep}
\section{Scholastic Achievements}
\vspace{\topsep}
\begin{tightemize}
\item Secured \textbf{All India Rank 3175} in JEE Advanced,2016 among 150,000 students.
\item Ranked in Top 0.1\% among 1.5 million candidates in JEE Main ,2016.
\item Awarded Academics Excellence Award for consecutive 5 years. 
\end{tightemize}
\sectionsep


\section{Skills}
\location{Programming Languages}
\textbullet{} Java \textbullet{}  Python \textbullet{} C/C++ \textbullet{} MATLAB \textbullet{} HTML\textbullet{}  \LaTeX\\ 
\location{Softwares}
\textbullet{}Vivado \textbullet{} ISE Design Suite \textbullet{} Adobe Photoshop \textbullet{} Git \\ 
\location{DBMS}
\textbullet{} MySQL\\
\sectionsep

\section{Extra-curricular Activities}
\vspace{\topsep}
\begin{tightemize}
\item Representative of Photography and Films Club IIT Delhi.
\item Volunteer at BloodConnect.
\item Volunteer at NSS, IITD.
\item Secured 3rd Position in JukeBox '16(Western Music Band Competition).
\item Secured 3rd Position in Wetern Group Dance'17. 
\end{tightemize}
\sectionsep


\end{document}  \documentclass[]{article}